---
title: "Alcohol vs Seat choice"
author: "Alba Morales"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
I choose to sit in the backrow.  
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```


This boxplot shows that the people who drink heavily sit in the back.


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
This shows that people who sit in the back drink 3x's as much alcohol than people who sit the front or middle row. 

## Inferential Tests

## Conclusions


